Explainability and Adversarial Robustness for RNNs

### 2020-02-14 paper/paper.tex
Removed page numbering
Small changes

\thispagestyle{plain}
\pagestyle{plain}

@@

\item
Based on the insights gained by the feature importance and explainability methods, we finally propose two defense methods.
%develop a simple method for defending against adversaries who can manipulate arbitrary packets by simply leaving out potentially manipulable information from the classification process.
First, by simply leaving out manipulable features, we obtain a classifier which is slightly less accurate but is still useful to be deployed in a real scenario. Second,
by deploying an adversarial training procedure,
%AH. compared to other research about adversarial training, I dont feel that out approach is so special
%develop a custom adversarial training procedure which especially focuses on ease of use and low resource consumption and aims to keep the number of additionally introduced training hyperparameters low. With this novel strategy
we can reduce the attack surface and harden the resulting \gls{ids} while retaining all features and similar classification performance. % like for the original \gls{ml} model.
\end{itemize}

We make all the source code, data and figures freely available to enable reproducibility and encourage experimentation at \url{https://github.com/CN-TU/adversarial-recurrent-ids}.

>>>>

% \thispagestyle{plain}
% \pagestyle{plain}

@@

\item
Based on the insights gained by the feature importance and explainability methods, we finally propose two defense methods.
%develop a simple method for defending against adversaries who can manipulate arbitrary packets by simply leaving out potentially manipulable information from the classification process.
First, by simply leaving out manipulable features, we obtain a classifier which is slightly less accurate but is still useful to be deployed in a real scenario. Second,
by deploying an adversarial training procedure,
%AH. compared to other research about adversarial training, I dont feel that out approach is so special
%develop a custom adversarial training procedure which especially focuses on ease of use and low resource consumption and aims to keep the number of additionally introduced training hyperparameters low. With this novel strategy
we can reduce the attack surface and harden the resulting \gls{ids} while retaining all features and similar classification performance. % like for the original \gls{ml} model.
We show that the \gls{ars} is significantly higher for the hardened model. 
\end{itemize}

We make all the source code, data, trained machine learning models and figures freely available to enable reproducibility and encourage experimentation at \url{https://github.com/CN-TU/adversarial-recurrent-ids}.
